Bioinformatics Assignment 2

### 2016-02-03 bioinformatics/latex/a2.tex
biomatics stuff
all

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{marvosym} % Required for symbols in the colored box
\usepackage{ifsym} % Required for symbols in the colored box

@@

\title{Classical Mechanics Assignment 9}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

\begin{align*}
  \tau \frac{\partial\phi}{\partial t} &= -\frac{\delta G}{\delta \phi}\\
  \\
  \frac{\partial \tilde{u}}{\partial t} &= \nabla^2 u + F\frac{\partial \phi}{\partial t}\\
  \\
  G(\phi_{i,j}) &= V(\phi_{i,j}) + \frac{\delta^2(\nabla\phi_{i,j})^2}{2}\\
\end{align*}

>>>>

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{listings}

@@

\title{Bioinformatics Assignment 2}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

\section{Problem One: Scoring Alignments}
Here we are asked to compute the score for different given alignments.\\

\textbf{A.} 3\\
\textbf{B.} 1\\

\section{Problem Two: BLAST}

\section{Problem Four: Database size}
We use the definition of E-value to compute database size, using an E-value of $e^{-27}:\\

\begin{align*}
  m &= \frac{E2^{S'}}{n} = \frac{e^{-27}2^{121}}{150} = 3.3*10^{22}\\
\end{align*}

\section{Problem Seven: GC Content}
GC content is conserved when taking reverse complement, since Gs and Cs map to
each other.\\

For original probability $p_{N0}$ and reverse complement probability $P_N'$:\\

\begin{align*}
  p_{G0} &= p_C'\\
  p_{C0} &= p_G'\\
  p_G &= \frac{p_{G0} + p_G'}{2} = \frac{p_{G0} + p_{C0}}{2} = \frac{0.63}{2} = 0.315\\
  p_C &= 0.315\\
  p_A &= 0.185\\
  p_T &= 0.185\\
\end{align*}

\section{Problem Eight: MEME}
Here we enter some MEME commands to find motifs:\\
\textbf{A.} meme proteins.fasta -protein -mod zoops -minw 10\\
\textbf{B.} meme sequences.fa -rna -mod anr -minw 5 -maxw 10\\
\textbf{C.} meme cores.fasta -dna -mod oops -nmotifs 5 \# -revcomp not specified,
only search forward strand\\
